Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-04 paper/paper.tex

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\author{
Curtis Ullerich, Daniel Stiner, Brandon Maxwell\\
Department of Computer Science and Engineering\\
Iowa State University
Ames, Iowa, USA\\
\{curtisu,stiner,bmaxwell\}@iastate.edu\\
}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends.
It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
Using machine learning techniques, we analyze the accuracy of classifying whether tweets are part of the public opinion about a particular company or merely contain keywords related to the company.
%Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
%Classification purely by keyword filtering often suffers from a
%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
Our dataset consists of approximately 2,000 tweets of which 64\% are related to public opinion about the company Apple, Inc. The other 36\% are not, but still contain keywords related to the company.
Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
by using domain-specific tokenizers, while surprisingly showing decreases in classification accuracy for other standard preprocessing methods such as n-grams.%maybe?
\end{quote}
\end{abstract}

@@

\begin{figure*}[t!]
\centering
\includegraphics[height=7cm]{chart}
\caption{Accuracy Chart}
\label{fig:chart}
\end{figure*}

@@

>>>>

\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
\author{
Curtis Ullerich, Daniel Stiner, Brandon Maxwell\\
Department of Computer Science and Engineering\\
Iowa State University
Ames, Iowa, USA\\
\{curtisu,stiner,bmaxwell\}@iastate.edu\\
}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends.
It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or mearly contain keywords related to the company.
%Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
%Classification purely by keyword filtering often suffers from a
%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
Our dataset consists of approximately 2,000 tweets of which 64\% are related to public opinion about the company Apple, Inc. The other 36\% are not, but still contain keywords related to the company.
Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
by using domain-specific tokenizers, while surprisingly showing decreases in classification accuracy for other standard preprocessing methods such as n-grams.%maybe?
\end{quote}
\end{abstract}

@@

\begin{figure*}[t!]
\centering
\includegraphics[height=7cm]{chart}
\caption{Accuracy vs. Training Corpus Size for All Text Processing Combinations}
\label{fig:chart}
\end{figure*}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{chart_twitterVSwhitespace}
\caption{Accuracy With Stemming and Stopword Removal}
\label{fig:chart_twitterwhitespace}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{chart_twitterVSwhitespace_detailed}
\caption{Accuracy For Twitter and Whitespace Tokenizers}
\label{fig:chart_twitterwhitespace_detailed}
\end{figure}
